### 2017-07-11 Bright_Stars/Submission/submission2.tex
second submission version as sent to PLOS One

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{change}

@@

% Header and Footer with logo
\usepackage{last,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=3.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{1.25in}
\fancyfootoffset[L]{1.25in}
\lfoot{\sf PLOS}

@@

%% Misc. Packages
\usepackage{changes}
\definechangesauthor[name={George Chacko}, color=orange]{gc}
\setremarkmarkup{(#2)}
\usepackage{listings}

@@

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\scalebox{1.3}{
%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
%\end{adjustwidth}
\end{figure}

@@

\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We have built upon the work of Williams~\cite{bibWilliams} in several ways. Author disambiguation in their code was not addressed beyond clustering by last name and first names. Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data. We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data. Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our approach scales to over 100,000 articles and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as the new nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) is calculated from normalizing the nPIR metric for an researcher to the sum of the researcher's individual PIR scores for each network being studied. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch}, although other data related issues may well emerge.}

@@

\bibitem{bibKohler}
K\"ohler, G., Milstein, C.
\newblock { {C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
\newblock Nature. 1975 256: 495-497.

>>>>

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=3.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{1.25in}
\fancyfootoffset[L]{1.25in}
\lfoot{\sf PLOS}

@@

%% Misc. Packages
\usepackage[final]{changes}
\definechangesauthor[name={George Chacko}, color=orange]{gc}
\setremarkmarkup{(#2)}
\usepackage{listings}

@@

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\scalebox{1.3}{
%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer arcs of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
%\end{adjustwidth}
\end{figure}

@@

\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We have built upon the work of Williams~\cite{bibWilliams} by addressing author disambiguation through the use of Scopus authorIDs and enriching the network data with grants and peer review data. Whereas, the original code was designed to handle a single drug and was not applied to a problem larger than 5000 articles, our approach scales to over 100,000 articles and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as the new nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) normalizes the nPIR metric for an researcher to the sum of the researcher's individual PIR scores for each network being studied. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch}, although other data related issues may well emerge.}

@@

\bibitem{bibKohler}
K\"ohler, G., Milstein, C.
\newblock {{C}ontinuous cultures of fused cells secreting antibody of predefined specificity.}
\newblock Nature. 1975 256: 495-497.
